\propertitle

### 2019-11-18 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-17T17:07:11+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Before applying this notion to neuronal activity, however, we must keep in
mind that \emph{informational sufficiency is not preserved under sampling}:
if a probability distribution has some sufficient statistics, then its
marginals, such as the distribution for a sample, \emph{cannot} have the
same sufficient statistics, and vice versa; except for trivial cases such
as uniform probability distributions. % This generally holds also among
% different marginals: if a statistics is sufficient for some marginal, then
% it will not be sufficient for another marginal.
This impossibility is known in statistical mechanics: if a system is
described by a Gibbs state, its subsystems cannot be perfectly described by
Gibbs states \citep[\eg][and references therein]{maesetal1999}.
Mathematically this impossibility comes from the Pitman-Koopman theorem
\citep{koopman1936,pitman1936,darmois1935} connecting sufficient statistics
and the exponential family of distributions, and translates into the
general impossibility of solving a system of $n$ independent equations in
$m$ unknowns with more equations than unknowns, $n>m$
\citep[\sect~3.1]{portamanaetal2015}.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-11-18T10:30:55+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Before applying this notion to neuronal activity, however, we must keep in
mind that \emph{informational sufficiency is not preserved under sampling}:
if a probability distribution has some sufficient statistics, then its
marginals, such as the distribution for a sample, \emph{cannot} have the
same sufficient statistics, and vice versa; except for trivial cases such
as uniform probability distributions. % This generally holds also among
% different marginals: if a statistics is sufficient for some marginal, then
% it will not be sufficient for another marginal.
This impossibility is known in statistical mechanics: if a system is
described by a Gibbs state, its subsystems cannot be perfectly described by
Gibbs states \citep[\eg][and references therein]{maesetal1999}.
Mathematically this impossibility comes from the Pitman-Koopman theorem
mentioned above, and translates into the general impossibility of solving a
system of $n$ independent equations in $m$ unknowns with more equations
than unknowns, $n>m$ \citep[\sect~3.1]{portamanaetal2015}.
